
title: "Data Replication"
author: "Dani Antos"
date: "October 30, 2017"
output: html_document
---
```{r loading gender data into r}
library(curl)
f <- curl("https://raw.githubusercontent.com/dantos17/AN597-Notes/master/Gender.txt")
d <- read.table(f, header = TRUE, sep = "\t", stringsAsFactors = FALSE)
head(d)
#I GOT ITTTTTTTTT
```
[whatever they said](http://...link) to create hyperlink

```{r reference genesets}
library(dslice)
blah2<-load_gmt("c1.symbols.gmt")
blah2$gene_symbol #This works, but which one do I want? if any?
#this isn't working
names(blah2)
c2 <- load_gmt("c2.symbols.gmt")
c2
names(c2)
c2$set_name
p53_c2 <- load_gmt("P53_C2.all.leading.genes.WT.gmt")
names(p53_c2)
names(c2)
df <- as.data.frame(blah2)
df$gene_symbol #this isn't working, it says there are different numbers of rows so I can't make a dataframe

```


```{r all gender data}
library(dslice)
library(GSA)
blah<-load_gct("Gender_hgu133a.gct")
blah
head(blah)
names(blah)
summary(blah)
real <- as.data.frame(blah)
real
names(real) #these are the same as the vector I made
genename <- real$NAME
genename #is there any way to get genenames without doing it by hand? maybe that's why I need the real one instead of the collapsed version # okay I'm doing it by hand fml
genename1 <- c("GM10832_0GY" , "GM10835_0GY" , "GM7057_0Y" , "GM13113_0GY" , "GM10860_0GY", "GM03187_0GY", "GM08390_0GY",  "GM09585_0GY", "GM09583_0GY", "GM00736_0GY", "GM03189_0GY", "GM09586_0GY", "GM0836_0GY", "GM13819_0GY", "GM00718_0GY", "NML37_0GY", "NML47_0GY", "NML50_0GY", "GM10833_0GY", "GM6990_0GY", "GM10834_0GY", "GM10861_0GY", "BR51_0GY", "BR258_0GY", "GM03188_0GY", "GM08388_0GY", "GM09579_0GY", "GM01526_0GY", "GM015785_0GY", "GM015786_0GY", "GM01525_0GY", "GM00719_0GY")
genename1
ds_gsa(blah, blah2, label= genename1)
GSA(blah, genesets = blah2, genenames = genename1) #OH YES I need the right geneset to compare against the dataset
gender_symbols <- load_gct("Gender_collapsed.gct")
summary(gender_symbols)
gender_cls <- load_cls("Gender.cls")
head(gender_cls)
summary(gender_cls) #this is working, but I don't think it's what I want...I think this is just a list of the males and females in the study

```

```{r all p53 data}
p53 <- load_gct("P53_hgu95av2.gct")
summary(p53)
p53_symbols <- load_gct("P53_collapsed_symbols.gct")
p53_symbols
summary(p53_symbols) #I think this one worked so I'm confused now
p53_real <- as.data.frame(p53_symbols)
genename_p53 <- p53_real[ ,0]
genename_p53
names(p53_real) #I don't want names I want the first column in a vector
p53_cls <- load_cls("P53.cls")
p53_cls1 <-  c("MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "MUT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT", "WT")
p53_cls1

GSA(p53_symbols, p53_cls1, genesets = c2, genenames = genename_p53) #NAMES ARE CELL LINES not genes
```


```{r importing other 2 datasets}
library(dslice)
library(GSA)
diabetes <- load_gct("Diabetes_hgu133a.gct")
summary(diabetes)
leukemia <- load_gct("Leukemia_hgu95av2.gct")
summary(leukemia)
```
So I can get everything into R but nothing is happening. Here's what I tried so far (all with **GENDER** data-- I think)

- I tried to do "blah$NAME" to get all of the genenames; *ERROR MESSAGE* it isn't in a dataframe format, so I made it into a dataframe using as.data.frame(), which worked, but the output for that was just "NULL"

- Made a vector using the names provided in the matrix (GM[number] etc.) as "genenames"

- Ran GSA (from {GSA} package) using blah as data, blah2 as geneset, and genename1 as genenames; *ERROR MESSAGE* fewer than 5% of genes in the geneset appear in the dataset, which makes sense at first glance, but I'm pretty sure they use C1 in the paper to compare against gender so that shouldn't be happening

- Ran ds_gsa (from {dslice} package) using the same inputs as GSA; *ERROR MESSAGE* 'description' argument is invalid, but I checked the documentation and there isn't any argument for description so I don't know what this means or how to fix it

- Ran GSA again; *ERROR MESSAGE* make sure that gene identifiers in dataset are Gene symbols, so I'm thinking that the dataset and geneset don't match, which would mean that I need to use the collapsed files

- Tried to upload the collapsed_symbol datasets into R; *ERROR MESSAGE* No such file or directory, cannot open the connection, I don't know how to fix this at all, I'm trying to open the geneset file to look at the names to try and manually fix the discrepancies

- I think there's just something wonky with the collapsed Gender file because I could upload the p53 collapsed file just fine, and now the names look more familiar. 

- Ran GSA on p53 collapsed file; *ERROR MESSAGE* same problem that I've been having with the 5% of genes, I tried using the other geneset (c2) and tried using "c2$gene_symbol" but nothing has been working (I also tried the other two "header" sections of the geneset)

- There is GSEA analysis data on the website but I'm having trouble interpreting it, I feel like they used different gene sets. I want to try using the "chr#p#" format for the genes but the datasets don't come in that format-- I still don't know whether the problem is the geneset or the genename


```{r}
GSEA.program.location <- "C://Users//dantos//Desktop//GSEA.1.0.R"   #  R source program (change pathname to the rigth location in local machine)
source(GSEA.program.location, verbose=T, max.deparse.length=9999)

GSEA(                                                                     # Input/Output Files :-------------------------------------------
 input.ds =  "C://Users//dantos//Downloads//Datasets//P53.gct",                 # Input gene expression Affy dataset file in RES or GCT format
 input.cls = "C://Users/dantos/Downloads/Datasets/P53.cls",                 # Input class vector (phenotype) file in CLS format
 gs.db =     "C://Users/dantos/Downloads/GeneSetDatabases/C2.gmt",          # Gene set database in GMT format
 output.directory      = "C://Users/dantos/Desktop/",              # Directory where to store output and results (default: "")
#  Program parameters :-------------------------------------------------------------------------------------------------------------------------
 doc.string            = "P53_C2",        # Documentation string used as a prefix to name result files (default: "GSEA.analysis")
 non.interactive.run   = F,               # Run in interactive (i.e. R GUI) or batch (R command line) mode (default: F)
 reshuffling.type      = "sample.labels", # Type of permutation reshuffling: "sample.labels" or "gene.labels" (default: "sample.labels" 
 nperm                 = 1000,            # Number of random permutations (default: 1000)
 weighted.score.type   =  1,              # Enrichment correlation-based weighting: 0=no weight (KS), 1= weigthed, 2 = over-weigthed (default: 1)
 nom.p.val.threshold   = -1,              # Significance threshold for nominal p-vals for gene sets (default: -1, no thres)
 fwer.p.val.threshold  = -1,              # Significance threshold for FWER p-vals for gene sets (default: -1, no thres)
 fdr.q.val.threshold   = 0.25,            # Significance threshold for FDR q-vals for gene sets (default: 0.25)
 topgs                 = 20,              # Besides those passing test, number of top scoring gene sets used for detailed reports (default: 10)
 adjust.FDR.q.val      = F,               # Adjust the FDR q-vals (default: F)
 gs.size.threshold.min = 15,              # Minimum size (in genes) for database gene sets to be considered (default: 25)
 gs.size.threshold.max = 500,             # Maximum size (in genes) for database gene sets to be considered (default: 500)
 reverse.sign          = F,               # Reverse direction of gene list (pos. enrichment becomes negative, etc.) (default: F)
 preproc.type          = 0,               # Preproc.normalization: 0=none, 1=col(z-score)., 2=col(rank) and row(z-score)., 3=col(rank). (def: 0)
 random.seed           = 760435,          # Random number generator seed. (default: 123456)
 perm.type             = 0,               # For experts only. Permutation type: 0 = unbalanced, 1 = balanced (default: 0)
 fraction              = 1.0,             # For experts only. Subsampling fraction. Set to 1.0 (no resampling) (default: 1.0)
 replace               = F,               # For experts only, Resampling mode (replacement or not replacement) (default: F)
 save.intermediate.results = F,           # For experts only, save intermediate results (e.g. matrix of random perm. scores) (default: F)
 OLD.GSEA              = F,               # Use original (old) version of GSEA (default: F)
 use.fast.enrichment.routine = T          # Use faster routine to compute enrichment for random permutations (default: T)
)
#--------------------------------------------------------------------------------------------------------------------------------------------------

# Overlap and leading gene subset assignment analysis of the GSEA results

GSEA.Analyze.Sets(
   directory           = "C://Users/dantos/Desktop/",             # Directory where to store output and results (default: "")
   topgs = 20,                                                           # number of top scoring gene sets used for analysis
   height = 16,
   width = 16
)
```

